---
title: "simpleRegress"
author: "Rashonda Weathersby"
date: "April 1, 2021"
output: 
 html_document:
  toc: true

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```
# NECK
## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
new <- data.frame(NECK=bears$NECK [c(5, 15, 23)])
predict(simp,new,se.fit=TRUE)
```


# HEADWTH
## Model LENGTH ~ HEADWTH  

```{r}
simphw <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simphw)
summary.lm(simphw)
```

```{r}
new <- data.frame(HEADWTH=bears$HEADWTH [c(5.5, 9, 8)])

predict(simphw,new,se.fit=TRUE)
```

# HEADLEN
## Model LENGTH ~ HEADLEN    


```{r}
simphl <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simphl)
summary.lm(simphl)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(11,16.5,15.5)])

predict(simphl,new,se.fit=TRUE)
```



# WEIGHT
## Model LENGTH ~ WEIGHT    


```{r}
simpwt <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpwt)
summary.lm(simpwt)
```


```{r}
new <- data.frame(WEIGHT=bears$WEIGHT[c(80,344,416)])

predict(simpwt,new,se.fit=TRUE)
```

# CHEST
## Model LENGTH ~ CHEST  


```{r}
simpct <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpct)
summary.lm(simpct)
```



## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(CHEST=bears$CHEST[c(26,45,54)])

predict(simpct,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

